A Cost-Aware Approach to Adversarial Robustness in Neural Networks

### 2024-09-02 main.tex
linting

We propose a methodology for model training and verification using accelerated failure-time (AFT) models, drawn from the field of \textit{survival analysis}, with a focus on cost-efficient evaluation methods.
AFT models are statistical models used to analyze multivariate effects on the observed failure rate to predict the time-to-failure across a wide variety of circumstances~\cite{aft_models,kleinbaum1996survival}. In medical science, these models are used to make claims like ``smokers are twice as likely to die from lung cancer'' or used to set the operating limits of manufactured components. This methodology can be used to map the relationship between various model tuning parameters and their effect on model performance.
The next section outlines the methodology for modelling the effect of model hyper-parameters during routine training procedures. We precisely outline the methodology for using survival analysis during the training of \acrshort{ml} methods.
% First, we present the proposed procedure in Algorithm~\ref{fig:alg} and a visual diagram of it in Figure~\ref{fig:experiments}. Then, in the sections below, we define accuracy (Section~\ref{acc}) and failure rate (Section~\ref{failure_rate}) in the context of survival analysis to make the concept of survival time clear (Section~\ref{survival_time}). We then discuss the importance of the ``acceleration assumption" (Section~\ref{accelerated}), the optimisation algorithm (Section~\ref{optimisation}), and the advantages of this approach (Section~\ref{advantages}).

@@

In security analysis, it is  routine to think in optimistic terms for both the attacker and defender. In cryptography, these ideal attack- and defence-scenarios are used to test the computational feasibility of subverting a particular cryptographic system~\cite{kamal2017study,leurent2020sha} (\textit{e.g.}, whether or not a given cryptographic method should be considered ``broken").
Using \acrshort{aft}, one can model the Pareto front --- the set of points that are superior to all others in the search space --- for all objectives~\cite{zitzler2008quality}.
By using a whitebox attack to generate the failures, we ensure that our defender operates under the worst case scenario while the attacker operates under their best case scenario to yield a worst-case failure rate.
As such, we center our analysis on the whitebox Fast Gradient Method (\acrshort{fgm})~\cite{fgm} (see Eq.~\ref{eq:fgm}) which is both effective and fast~\cite{meyers}. If the cost to a model builder is much larger than the cost to an attacker, then it is  clear that the model is ``broken" in this cryptographic sense and can be discarded as ineffective~\cite{meyers_aft}. \cm{Figure~\ref{fig:trash} depicts the TRASH score defined in Equation~\ref{eq:cost}, that quantifies the per-sample ratio of training to attack time. It is clear that even with the reduced GPU bandwidth (Table~\ref{tab:hardware}), that the L4 model is not only superior in terms of cost (Table~\ref{tab:hardware}), but also in terms of robustness (Table~\ref{tab:hardware}), presumably since the extra bit-depth provided by the P100 and V100 ends up being useless noise anyway when operating on 8-bit images like MNIST and CIFAR.}

@@

\cm{
Regardless of which AFT model is chosen, the model suggests that the P100 decreases the survival time compared to the V100 and the L4 increases the survival time (both compared to the V100, which has no significant effect).
Furthermore, the coefficients again confirm an inverse relationship between test-set (benign) accuracy and the adversarial robustness (\textit{i.e.} survival time).
Finally, even when we account for the reduced GPU bandwidth (see: Table~\ref{tab:hardware}) and increased training time (see: Figure~\ref{fig:time}), it is clear the the L4 model is superior in terms of robustness and cost-effectiveness (see: Figure~\ref{fig:trash}), despite it being advertised as ``inference only" by the manufacturer.
}
Furthermore, the data demonstrate the un-advertised training capability of the Nvidia L4 GPU which yields a 20\% increase in survival time while costing 75\% less than the V100 that's been typical in the literature over the last several years.

>>>>

We propose a methodology for model training and verification using accelerated failure-time (AFT) models, drawn from the field of \textit{survival analysis}, with a focus on cost-efficient evaluation methods.
AFT models are statistical models used to analyze multivariate effects on the observed failure rate to predict the time-to-failure across a wide variety of circumstances~\cite{aft_models,kleinbaum1996survival}. In medical science, these models are used to make claims like ``smokers are twice as likely to die from lung cancer'' or used to set the operating limits of manufactured components. This methodology can be used to map the relationship between various model tuning parameters and their effect on model performance.
The next section outlines the methodology for modelling the effect of model hyper-parameters during routine training procedures. We precisely outline the methodology for using survival analysis during the training of \acrshort{ml} methods.
% First, we present the proposed procedure in Algorithm~\ref{fig:alg} and a visual diagram of it in Figure~\ref{fig:experiments}. Then, in the sections below, we define accuracy (Section~\ref{acc}) and failure rate (Section~\ref{failure_rate}) in the context of survival analysis to make the concept of survival time clear (Section~\ref{survival_time}). We then discuss the importance of the ``acceleration assumption'' (Section~\ref{accelerated}), the optimisation algorithm (Section~\ref{optimisation}), and the advantages of this approach (Section~\ref{advantages}).

@@

In security analysis, it is  routine to think in optimistic terms for both the attacker and defender. In cryptography, these ideal attack- and defence-scenarios are used to test the computational feasibility of subverting a particular cryptographic system~\cite{kamal2017study,leurent2020sha} (\textit{e.g.}, whether or not a given cryptographic method should be considered ``broken'').
Using \acrshort{aft}, one can model the Pareto front --- the set of points that are superior to all others in the search space --- for all objectives~\cite{zitzler2008quality}.
By using a whitebox attack to generate the failures, we ensure that our defender operates under the worst case scenario while the attacker operates under their best case scenario to yield a worst-case failure rate.
As such, we center our analysis on the whitebox Fast Gradient Method (\acrshort{fgm})~\cite{fgm} (see Eq.~\ref{eq:fgm}) which is both effective and fast~\cite{meyers}. If the cost to a model builder is much larger than the cost to an attacker, then it is  clear that the model is ``broken'' in this cryptographic sense and can be discarded as ineffective~\cite{meyers_aft}. \cm{Figure~\ref{fig:trash} depicts the TRASH score defined in Equation~\ref{eq:cost}, that quantifies the per-sample ratio of training to attack time. It is clear that even with the reduced GPU bandwidth (Table~\ref{tab:hardware}), that the L4 model is not only superior in terms of cost (Table~\ref{tab:hardware}), but also in terms of robustness (Table~\ref{tab:hardware}), presumably since the extra bit-depth provided by the P100 and V100 ends up being useless noise anyway when operating on 8-bit images like MNIST and CIFAR.}

@@

\cm{
Regardless of which AFT model is chosen, the model suggests that the P100 decreases the survival time compared to the V100 and the L4 increases the survival time (both compared to the V100, which has no significant effect).
Furthermore, the coefficients again confirm an inverse relationship between test-set (benign) accuracy and the adversarial robustness (\textit{i.e.} survival time).
Finally, even when we account for the reduced GPU bandwidth (see: Table~\ref{tab:hardware}) and increased training time (see: Figure~\ref{fig:time}), it is clear the the L4 model is superior in terms of robustness and cost-effectiveness (see: Figure~\ref{fig:trash}), despite it being advertised as ``inference only'' by the manufacturer.
}
Furthermore, the data demonstrate the un-advertised training capability of the Nvidia L4 GPU which yields a 20\% increase in survival time while costing 75\% less than the V100 that's been typical in the literature over the last several years.
